Automated Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-03 paper/paper_new.tex
Updates from Overleaf

\title{Automated Metadata Generation for Fish Specimen Image Collections%*\\
    {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }}
%do we add grant now, or wait til acceptance. i think we need to ultimately remove any identifying info., i think bgnn is likely okay; but, perhaps mention metadata research center (MRC) need to be removed?. if so, i kind of like to put it back in for final version, if accepted. it helps with getting funding ... you are both listed on the MRC page. we should check on the identifying info. removed, or not.
%for the record: Research supported by NSF OAC #1940233 and #1940322.

@@

%abstract can be shortened a good bit.
%can offer an alternative manana..
\begin{abstract}
Metadata is a key data source particularly for researchers seeking use [apply] machine learning to the vast collections of digitized specimens. Unfortunately, the metadata available is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual [*human] means. This paper reports on a research applying machine-driven [*automatic] approaches to analyze digitized fish images and extract a variety of important features. The digitized fish specimen are being analyzed as part of Biology Guided Neural Networks (BGNN) initiative, where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies. The paper reports on research combining machine  learning  and  image  informatics tools and techniques. A sample 7244 images from the Illinois Natural History Survey (INHS) were examined via automatic processes [*<--needs help]. Results show we can  accurately extract metadata, such as, fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics. Results also indicate that automatic approaches "can outperform humans" [*and/or "expedite"] the creation of metadata that's critical to leveraging digitized specimens for machine learning. The sections that follow cover background context, reviews the research design, reports results Next,  the  results  are presented, followed by a discussion. 
%items in square brackets [*xxx] are just other suggested words, e.g., select one or the other, or ....
%let's give a few data results, e.g., percentages, numbers..what will be emphasize in conclusion, key findings.
%abstract could say something about comparison to human results.

% Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery. One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.The metadata that is vital for subsequent machine learning, analysis and scientific discovery based on these specimen image repositories is often unavailable, sparse or incorrect. As a step towards improving metadata in specimen research image collections, our team is developing methods for automatically analyzing fish images to extract a variety of important features. These fish specimens are being studied for a larger project entitled Biology Guided Neural Networks (BGNN), which is developing a novel class of artificial neural networks that can exploit the machine readable and predictive knowledge about biology that is available in specimen images, phylogenies and anatomy ontologies. Using a combination of machine learning and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.Our goal is to develop image metadata generation methods that both support the research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images. A longer term goal is to extend the image analysis methods for computing quantitative features in support of specific biological investigations.
\end{abstract}

>>>>

\title{Automated Metadata Generation for Fish Specimen Image Collections%*\\
    {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }}

@@

%abstract can be shortened a good bit.
%can offer an alternative manana..
\begin{abstract}
Metadata is a key data source particularly for researchers seeking use [apply] machine learning to the vast collections of digitized specimens. Unfortunately, the metadata available is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual [*human] means. This paper reports on a research applying machine-driven [*automatic] approaches to analyze digitized fish images and extract a variety of important features. The digitized fish specimen are being analyzed as part of Biology Guided Neural Networks (BGNN) initiative, where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies. The automatically generated metadata is crucial for identifying high-quality images for the neural network, and, further support empirical [*predicative] analysis [analytics?]. This paper reports specifically on research combining machine learning  and  image  informatics tools and techniques. A sample 7244 images from the Illinois Natural History Survey (INHS) were examined via automatic processes [*<--needs help]. Key findings indicate z, y, z.
%for x, y, z, can we give some numbers? thinking on this.
Results show we can  accurately extract metadata, such as, fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics. Results also indicate that automatic approaches "can outperform humans" [*and/or "expedite"] the creation of metadata that's critical to leveraging digitized specimens for machine learning. This research has implications for leveraging the extensive collection of digitized scientific images stored in globally, accessible open repositories.
%[another way to make this last sentence, so we can use the word novel?] the research presented here offers a novel approach for leveraging.

% OLD text - Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery. One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.The metadata that is vital for subsequent machine learning, analysis and scientific discovery based on these specimen image repositories is often unavailable, sparse or incorrect. As a step towards improving metadata in specimen research image collections, our team is developing methods for automatically analyzing fish images to extract a variety of important features. These fish specimens are being studied for a larger project entitled Biology Guided Neural Networks (BGNN), which is developing a novel class of artificial neural networks that can exploit the machine readable and predictive knowledge about biology that is available in specimen images, phylogenies and anatomy ontologies. Using a combination of machine learning and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.Our goal is to develop image metadata generation methods that both support the research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images. A longer term goal is to extend the image analysis methods for computing quantitative features in support of specific biological investigations.
\end{abstract}
